Poseidon Adventure

### 2020-03-18 NOBAcod.Rmd
start on wrapping NOBA cod

---
title: "Generate data for NOBA cod ensemble modeling"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

We need config files for the NOBA model, our surveys and fisheries.

`NOBAconfig.R` looks like this (adjusted from Alfonso's original):

---
d.name <- here("atlantisoutput","NOBA_march_2020")
functional.groups.file <- "nordic_groups_v04.csv"
biomass.pools.file <- "nordic_biol_v23.nc"
biol.prm.file <- "nordic_biol_incl_harv_v_007_3.prm"
box.file <- "Nordic02.bgm"
initial.conditions.file <- "nordic_biol_v23.nc"
run.prm.file <- "nordic_run_v01.xml"
scenario.name <- "nordic_runresults_01"
bioind.file <- "nordic_runresults_01BiomIndx.txt"
catch.file <- "nordic_runresults_01Catch.txt"
---

@@

---
timeall <- c(0:560)

funct.group.indices <- c(1:36)
---

@@

---

---

@@

```{r full-test}

@@

NOBAom <- om_init(here("config/NOBAconfig.R"))

NOBAom_cod <- om_species(c("Pacific_sardine"), NOBAom)

NOBAom_cod_ind <- om_index(usersurvey = here("config/sardinesurvey.R"), 
                           userfishery = here("config/sardinefishery.R"),
                           omlist_ss = CC3om_sardine, 
                           n_reps = 1, 
                           save = TRUE)

NOBAom_cod_comp <- om_comps(usersurvey = here("config/sardinesurvey.R"), 
                           userfishery = here("config/sardinefishery.R"),
                           omlist_ss = CC3om_sardine, 
                           n_reps = 1, 
                           save = TRUE)

@@

Use the saved outputs of above to write a Stock Synthesis dat file
This is not a function yet, copy in Christine's

**See corrections below, in fishery time fixed and nsamp added to length comps**

```{r writedat}

>>>>

---
title: "Generate data for NOBA cod ensemble modeling"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

We need config files for the NOBA model, our surveys and fisheries. Surveys and fisheries are based on the ones we used for sardine in the California Current as a test.

*Special note: Atlantis output files usually have the prefix "output" and `atlantisom` expects this. NOBA output files use a different naming convention. I've appended "output" to the beginning of each NOBA output filename for `atlantisom` to work.*

`NOBA2config.R` looks like this (adjusted from Alfonso's original):

```
d.name <- here("atlantisoutput","NOBA_march_2020")
functional.groups.file <- "nordic_groups_v04.csv"
biomass.pools.file <- "nordic_biol_v23.nc"
biol.prm.file <- "nordic_biol_incl_harv_v_007_3.prm"
box.file <- "Nordic02.bgm"
initial.conditions.file <- "nordic_biol_v23.nc"
run.prm.file <- "nordic_run_v01.xml"
scenario.name <- "nordic_runresults_01"
bioind.file <- "outputnordic_runresults_01BiomIndx.txt"
catch.file <- "outputnordic_runresults_01Catch.txt"
```

`omdimensions.R` standardizes timesteps, etc.:

```
#survey species inherited from omlist_ss
survspp <- omlist_ss$species_ss
# survey season and other time dimensioning parameters
# generalized timesteps all models
noutsteps <- omlist_ss$runpar$tstop/omlist_ss$runpar$outputstep
timeall <- c(0:noutsteps)
stepperyr <- if(omlist_ss$runpar$outputstepunit=="days") 365/omlist_ss$runpar$toutinc
midptyr <- round(median(seq(0,stepperyr)))

# model areas, subset in surveyconfig
allboxes <- c(0:(omlist_ss$boxpars$nbox - 1))

# fishery output: learned the hard way this can be different from ecosystem outputs
fstepperyr <- if(omlist_ss$runpar$outputstepunit=="days") 365/omlist_ss$runpar$toutfinc

# survey selectivity (agecl based)
# should return all age classes fully sampled (Atlantis output is 10 age groups per spp)
n_age_classes <- omlist_ss$funct.group_ss$NumCohorts
age_classes <- 1:n_age_classes

n_annages <- n_age_classes * omlist_ss$funct.group_ss$NumAgeClassSize
annages <- 1:n_annages

@@

```
# Default survey configuration here is a census
# Need to define survey season, area, efficiency, selectivity

#Atlantis model timestep corresponding to the true output--now from census_spec.R
timestep <- stepperyr #5

#Which atlantis timestep does the survey run in?--now from census_spec.R
# with 5 output steps per year, 0 is Jan-Feb-midMar, 1 is midMar-Apr-May, 
# 2 is June-July-midAug, 3 is midAug-Sept-Oct, 4 is Nov-Dec (ish)

survey_sample_time <- midptyr #2; defined in omdimensions.R

#The last timestep to sample
total_sample <- noutsteps-1 #495

#Vector of indices of survey times to pull
survey_sample_full <- seq(survey_sample_time,
                          total_sample, by=timestep)

survtime <- survey_sample_full

# survey area
# should return all model areas
survboxes <- allboxes

# survey efficiency (q)
# should return a perfectly efficient survey 
surveffic <- data.frame(species=survspp,
                     efficiency=rep(0.5,length(survspp)))

# survey selectivity (agecl based)
# this is by age class, need to change to use with ANNAGEBIO output
survselex <- data.frame(species=rep(survspp, each=n_age_classes),
                     agecl=rep(c(1:n_age_classes),length(survspp)),
                     selex=rep(1.0,length(survspp)*n_age_classes))

# effective sample size needed for sample_fish
# this effective N is high but not equal to total for numerous groups
surveffN <- data.frame(species=survspp, effN=rep(1000, length(survspp)))

# survey index cv needed for sample_survey_xxx
# cv = 0.1
surv_cv <- data.frame(species=survspp, cv=rep(0.1,length(survspp)))

# length at age cv for input into calc_age2length function
# function designed to take one cv for all species, need to change to pass it a vector
lenage_cv <- 0.1

# max size bin for length estimation, function defaults to 150 cm if not supplied
maxbin <- 150

@@

```
# Default fishery configuration here is a census
# Inherits species from input omlist_ss
fishspp <- omlist_ss$species_ss

#Number of years of data to pull
nyears <- 50

#Atlantis initialization period in years
burnin <- 30

# same time dimensioning parameters as in surveycensus.R
#Vector of indices of catch in numbers to pull (by timestep to sum)
fish_sample_full <- c(0:total_sample)  #total_sample defined in sardinesurvey.R
fish_burnin <- burnin*fstepperyr+1
fish_nyears <- nyears*fstepperyr
fish_times <- fish_sample_full[fish_burnin:(fish_burnin+fish_nyears-1)]
fish_timesteps <- seq(fish_times[5], max(fish_times), by=fstepperyr) #last timestep
#fish_years <- unique(floor(fish_times/fstepperyr)+1) # my original
fish_years <- unique(floor(fish_times/fstepperyr)) #from Christine's new sardine_config.R

fishtime <- fish_times

# fishery output: learned the hard way this can be different from ecosystem outputs
fstepperyr <- if(omlist_ss$runpar$outputstepunit=="days") 365/omlist_ss$runpar$toutfinc

# fishery sampling area
# should return all model areas, this assumes you see everything that it caught
fishboxes <- c(0:(omlist_ss$boxpars$nbox - 1))

# effective sample size needed for sample_fish
# this effective N is high but not equal to total for numerous groups
fisheffN <- data.frame(species=survspp, effN=rep(1000, length(survspp)))

#this adjusts for subannual fishery output so original effN is for whole year
fisheffN$effN <- fisheffN$effN/fstepperyr

# fishery catch cv can be used in sample_survey_biomass
# perfect observation
fish_cv <- data.frame(species=survspp, cv=rep(0.01,length(survspp)))
```

@@

```{r full-test, eval=FALSE}

@@

NOBAom <- om_init(here("config/NOBA2config.R"))

NOBAom_cod <- om_species(c("North_atl_cod"), NOBAom)

NOBAom_cod_ind <- om_index(usersurvey = here("config/codsurvey.R"), 
                           userfishery = here("config/codfishery.R"),
                           omlist_ss = NOBAom_cod, 
                           n_reps = 1, 
                           save = TRUE)

NOBAom_cod_comp <- om_comps(usersurvey = here("config/sardinesurvey.R"), 
                           userfishery = here("config/sardinefishery.R"),
                           omlist_ss = NOBAom_cod, 
                           n_reps = 1, 
                           save = TRUE)

@@

We will need to alter this for SAM, SS3, etc. Right now just makes SS3.

**THIS IS STILL THE CALIFORNIA CURRENT INFO, TO BE UPDATED**

```{r writedat, eval=FALSE}

### 2020-03-18 docs/index.Rmd
begin wrapper functions
wrappers to initialize and split species so far
test wrappers with changed config files
writing dat file now from proto-SS write wrapper
start on wrapping NOBA cod

>>>>

### Apply wrapper to Norwegian Barents cod, March 2020

<a href="https://sgaichas.github.io/poseidon-dev/NOBAcod.html" target="_blank">Apply and extend wrappers to get full age structure, started March 18, 2020</a>

### Working on wrapper functions, January 2020

<a href="https://sgaichas.github.io/poseidon-dev/WrapperDevelopment.html" target="_blank">Automating om functions to streamline workflows, January 17, 2020 writes dat file as of March 16, 2020</a>
